Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 thesis/thesis.tex
Adding some more content to the results section, adding a bit more of a description to the results. Remove redundant question.
Moving tables out into separate files and formatting widths a bit cleaner
Spacing

Onion routing was originally developed by the U.S. Naval Research Lab in 1996
\parencite{Goldschlag:1996wy} for application by the U.S. Navy. Like a mix,
messages sent over an onion routing network were encrypted with their routing
information and delivered to an intermediate server for forward delivery.
Unlike the mix however, messages delivered using the onion routing network were
encrypted multiple times, each 'layer' using a different key and routing
instructions. The first node in a chain would only be able to encrypt the
routing instructions to deliver the message to the next node. Each node in the
sequence decrypting a layer until the complete message is decrypted and
transmitted to the destination. This invention was granted a patent by the U.S.
Patent Office in 2001 \parencite{Michael:2001}.

@@

\begin{enumerate*}
  \item Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?
  \item Does Tor traffic have characteristics that make it distinguishable using
    machine learning techniques?
\end{enumerate*}

>>>>

Onion routing was originally developed by the U.S. Naval Research Lab in 1996
\parencite{Goldschlag:1996wy} for application by the U.S. Navy. Like a mix,
messages sent over an onion routing network were encrypted with their routing
information and delivered to an intermediate server for forward delivery.
Unlike the mix however, messages delivered using the onion routing network were
encrypted multiple times, each 'layer' using a different encryption key and
routing instructions. The first node in a chain would only be able to encrypt
the routing instructions to deliver the message to the next node. Each node in
the sequence decrypting a layer until the complete message is decrypted and
transmitted to the destination. This invention was granted a patent by the U.S.
Patent Office in 2001 \parencite{Michael:2001}.

@@

\begin{enumerate*}
  \item Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?
\end{enumerate*}
